Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-21 paper.tex

>>>>

We measure CPU time via the procfs using the same methodology as the
\texttt{top} utility. The \texttt{/proc/[pid]/stat} file for kswapd is read.
From this file the \texttt{utime} and \texttt{stime} fields are read and summed
to get the total time allocated to kswapd. Then, the \texttt{/proc/stat} file is
read to get the total system time elapsed. By dividing, we can find the portion
of CPU time spent in kswapd.
